Renewal and stability in populations structured by remaining years of life

### 2014-11-22 ThanoRepro/ThanoRepro.tex
maybe something is broken in tikz. will need to handle it on laptop...
generated figs, fixed tikz to current version, slight change in sentence in damping. Need to think more about how far to go in results based on unstable populations, introduce the concept clearer

\documentclass{article}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage{pgf}
\usepackage{tikz}
%\usetikzlibrary{arrows}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture}
%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}

@@

\begin{figure}
\centering
\caption{The thanatological lifecycle graph}
\label{fig:graph}
\begin{tikzpicture}[->,shorten>=1pt,auto,node distance=4.3cm,thick,main
node/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]
  \definecolor{gray}{rgb}{0.8,0.8,0.8}
  \definecolor{lightgreen}{rgb}{0,0.8,0.8}

@@

From the projection matrix, the ratio of the largest to the second largest
eigenvalue, the damping ratio, is an indicator of the \textit{springiness} of
the stable population structure, $c^\star(y)$ or $c(a)$, with respect to
disturbances from the stable state as determined by vital rate distributions. A
higher damping ratio means that the population structure oscillates back to
its stable state faster, i.e., that oscillations decrease in size more rapidly. The thanatological damping ratio was
greater than the Leslie damping ratio for all 1834 population-years included in
our empirical analysis. Leslie damping ratios ranged from 1.01258 to 1.0518,
while thanatological damping ratios ranged from 1.0455 to 1.0868. Again, this
was for the raw data, and I am not sure whether this consistent finding is a
natural property of the model or an artifact of the unstable starting state of
the data used to derive thanatological fertility rates. Intuitively, the
thanatological smoothing process should be an order of magnitude stronger than
the chronological smoothing process because each thanatological age class
(node) -- except for the oldest-old -- is connected directly to each other
thanatological age class in both directions. Again, I think contrived examples
will be necessary to shed more light on this finding.

>>>>

\documentclass{article}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture}
%\setlength\PreviewBorder{5pt}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}
\newcommand{\ec}{\quad\quad\text{,}}
\newcommand{\ep}{\quad\quad\text{.}}

@@

\begin{figure}
\centering
\caption{The thanatological lifecycle graph}
\label{fig:graph}
\begin{tikzpicture}[->,auto,node distance=4.3cm,thick,main
node/.style={circle,fill=blue!20,draw,font=\sffamily\Large\bfseries}]
  \definecolor{gray}{rgb}{0.8,0.8,0.8}
  \definecolor{lightgreen}{rgb}{0,0.8,0.8}

@@

From the projection matrix, the ratio of the largest to the second largest
eigenvalue, the damping ratio, is an indicator of the \textit{springiness} of
the stable population structure, $c^\star(y)$ or $c(a)$, if perturbed from the
state of stability.
A higher damping ratio means that the population structure oscillates back to
its stable state faster, i.e., that oscillations decrease in size more rapidly. The thanatological damping ratio was
greater than the Leslie damping ratio for all 1834 population-years included in
our empirical analysis. Leslie damping ratios ranged from 1.01258 to 1.0518,
while thanatological damping ratios ranged from 1.0455 to 1.0868. Again, this
was for the raw data, and I am not sure whether this consistent finding is a
natural property of the model or an artifact of the unstable starting state of
the data used to derive thanatological fertility rates. Intuitively, the
thanatological smoothing process should be an order of magnitude stronger than
the chronological smoothing process because each thanatological age class
(node) -- except for the oldest-old -- is connected directly to each other
thanatological age class in both directions. Again, I think contrived examples
will be necessary to shed more light on this finding.
